Nail: A practical interface generator for data formats

### 2015-08-17 paper/thesis/concl.tex
DNS CPP benchmark
paper->thesis

\section{Conclusion}
\label{s:concl}

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
establishing a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software, available at
\url{https://github.com/jbangert/nail}.

>>>>

\chapter{Conclusion}
\label{s:concl}

This thesis presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
establishing a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this thesis
are released as open-source software, available at
\url{https://github.com/jbangert/nail}.

### 2015-08-17 paper/thesis/intro.tex
thesis
paper->thesis

\section{Introduction}

@@

This paper presents the design and implementation of Nail, a parser generator that greatly reduces
the programmer effort required to use grammars. Nail addresses the above challenges with
several key ideas, as follows.

@@

The rest of this paper is organized as follows.  \S\ref{s:relwk}
puts Nail in the context of related work.
\S\ref{s:motivation} motivates the need for Nail by examining
past data format vulnerabilities.
\S\ref{s:design} describes
Nail's design.  \S\ref{s:impl} discusses our implementation
of Nail.  \S\ref{s:eval} provides evaluation results, and
\S\ref{s:concl} concludes.

>>>>

\chapter{Introduction}

@@

This thesis presents the design and implementation of Nail, a parser generator that greatly reduces
the programmer effort required to use grammars. Nail addresses the above challenges with
several key ideas, as follows.

@@

The rest of this thesis is organized as follows.  \S\ref{s:relwk}
puts Nail in the context of related work.
\S\ref{s:motivation} motivates the need for Nail by examining
past data format vulnerabilities.
\S\ref{s:design} describes
Nail's design.  \S\ref{s:impl} discusses our implementation
of Nail.  \S\ref{s:eval} provides evaluation results, and
\S\ref{s:concl} concludes.
